\vskip-0.6in Endogenous Politics and the Design of Trade Institutions

### 2016-07-25 feedback.tex
integrate Ryerson feedback into to-do
add ETSG 2014 and McGill feedback to to-do

\subsection{Sept. 12, 2014, ETSG}
\begin{itemize}
	\item Paola: How do I want to sell the paper?
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\item Baldwin-style welfare function works for a set of questions, but not for this one
			\item GH is isomorphic
		\end{itemize}
	\item Coates Ludema 2001
		\begin{itemize}
			\item What if WTO actually \textit{did} what literature says it does? It wouldn't work!
			\item Be more explicit about the relationship between $\ga(e)$ and $\ga(s)$
		\end{itemize}
	\item I need to be able to say which questions are okay with
		\begin{enumerate}
			\item unweighted/standard welfare function
			\item $\ga(s)$ only (i.e. predictions/design predictions won't change lobbying incentives) 
		\end{enumerate}
\end{itemize}

\subsection{Oct. 17, 2014, McGill}
\begin{itemize}
	\item Hanson and Sargent, model uncertainty
	\item Why Nash bargain for tariff cap?
\end{itemize}

\subsection{Nov. 7, 2014, Ryerson}
\begin{itemize}
	\item Export lobby at ex-post b/c wants to reduce chance of trade war
	\item $e$ in terms of numeraire
	\item Could escape clause be made to work with some fancier set up, e.g. dynamic use constraint?
\end{itemize}

>>>>

\subsection{Sept. 12, 2014, ETSG}
\begin{itemize}
	\item Paola: How do I want to sell the paper? [on to-do list]
		\begin{itemize}
			\item In relation to what literature?
				\begin{itemize}
					\item What literature does endogenous? Coates-Ludema 2001, MRC, GH
					\item What literature \textit{doesn't}?
				\end{itemize}
			\item Baldwin-style welfare function works for a set of questions, but not for this one [DONE]
			\item GH is isomorphic [on to-do list]
		\end{itemize}
	\item Coates Ludema 2001 [on to-do list]
		\begin{itemize}
			\item What if WTO actually \textit{did} what literature says it does? It wouldn't work! [done]
			\item Be more explicit about the relationship between $\ga(e)$ and $\ga(s)$ [done]
		\end{itemize}
	\item I need to be able to say which questions are okay with [done]
		\begin{enumerate}
			\item unweighted/standard welfare function
			\item $\ga(s)$ only (i.e. predictions/design predictions won't change lobbying incentives) 
		\end{enumerate}
\end{itemize}

\subsection{Oct. 17, 2014, McGill}
\begin{itemize}
	\item Hanson and Sargent, model uncertainty [doesn't seem that relevant]
	\item Why Nash bargain for tariff cap? [why not?]
\end{itemize}

\subsection{Nov. 7, 2014, Ryerson}
\begin{itemize}
	\item Export lobby at ex-post b/c wants to reduce chance of trade war [outside the scope of this paper]
	\item $e$ in terms of numeraire [on to-do list]
	\item Could escape clause be made to work with some fancier set up, e.g. dynamic use constraint? [on to-do list]
\end{itemize}
